---
title: ""
output: github_document
---

# Data

Federal payroll records obtained from the U.S. Office of Personnel Management by [Buzzfeed](https://www.buzzfeed.com/jsvine/sharing-hundreds-of-millions-of-federal-payroll-records?utm_term=.xr93XYlojJ#.tlqXR12zrO)

There are three sets of data (as of Dec 2017): 1973-09 to 2014-06, 2014-09 to 2016-09, and 2016-12 to 2017-03. 

## How to read the data

### 1973-2014

These are fixed-width files. You need to specify the width of each column to read the file. The widths can be found in [this letter](https://ia600608.us.archive.org/16/items/opm-federal-employment-data/docs/2015-02-11-opm-foia-response.pdf). *However*, the [`Years Since Degree Range` column is missing in the "status" files](https://archive.org/details/opm-federal-employment-data).

Example code to read in a "status" file from 1973-2014:

```{r, eval = FALSE}

library(readr)

widths = c(9, 23, 8, 4, 9, 6, 2, 2, 2, 6, 4, 1, 6, 1, 2, 1, 1)

varnames = c("id", "name", "filedate", "agency_subelement", "duty_station", "age_range", "education", "payplan", "grade", "los", "occupation", "occupational_category", "adjusted_basic_pay", "supervisory_status", "appointment_type", "work_schedule", "nsftp")

root = ""
dir = paste0(root, "opm-federal-employment-data/data/1973-09-to-2014-06/non-dod/status/",
             "Status_Non_DoD_2009_12.txt")

status = read_fwf(dir, fwf_widths(widths, varnames), na = c("", "NA", "*"))

```

Example code to read in a "dynamic" file from 1973-2014:

```{r, eval = FALSE}

widths = c(9, 23, 4, 2, 8, 6, 2, 2, 6, 9, 4, 1, 6, 2, 1)

varnames = c("id", "name", "agency_subelement", "access_separate", "effective_date", "age", "payplan", "grade", "los", "duty_station", "occupation", "occupational_category", "adjusted_basic_pay", "appointment_type", "work_schedule")

root = ""
dir = paste0(root, "opm-federal-employment-data/data/1973-09-to-2014-06/non-dod/dynamic/",
             "JUN1991.NONDOD.FO05M3.TXT")

dyn = read_fwf(dir, fwf_widths(widths, varnames), na = c("", "NA", "*", "**"))

```

