---
title: "Reading in 1973 to 2014 fixed-width data"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(tidyverse)
library(magrittr)
```

In general, the information needed to read in the different files seems to be available in the `documentation` or `docs` folders, particularly for the later sets of files. And if not they are available in the FOIA response letters, in particular the widths for the first set files starting 1973. 

### 1973-2014

These files are fixed-width. Width lengths are specified in [this doc dated 2015-02-11](https://ia600608.us.archive.org/16/items/opm-federal-employment-data/docs/2015-02-11-opm-foia-response.pdf). However, it is also noted at [this link](https://archive.org/details/opm-federal-employment-data) that the "Years Since Degree Range" column is missing, so exclude that when reading in the files. 

```{r}
dir = glue::glue(
  "/Volumes/research_data/opm-federal-employment-data/data/",
  "1973-09-to-2014-06/non-dod/status/",
  "Status_Non_DoD_2009_12.txt")

widths = c(9, 23, 8, 4, 9, 6, 6, 2, 2, 2, 6, 4, 1, 6, 1, 2, 1, 1)

varnames = c("id", "name", "filedate", "agency_subelement", "duty_station", "age_range", "years_since_degree_range", "education", "payplan", "grade", "los", "occupation", "occupational_category", "adjusted_basic_pay", "supervisory_status", "appointment_type", "work_schedule", "nsftp")

df_widths = data_frame(widths = widths, varnames = varnames)

df_widths %<>% filter(varnames != "years_since_degree_range")

df_fwf = read_fwf(dir, fwf_widths(df_widths$widths, df_widths$varnames), n_max = 5000, na = c("", "NA", "*"), 
                  col_types = cols())

df_fwf

```

I think the first column is an ID, then there's a name column which has been massacred in `X2` to `X4`. The numbers in `X5` are probably the date the data was released or something like that. `X8` is probaby age ranges, and somewhere in `X9` there's also a range for years since degree. The problematic parts are:

- Between `X5` and `X7`, I have no idea what the variables are how many of them there are. Seems like agency is in there somewhere but I don't know what else
- I can't tell what else is going on in `X9`, although after talking to you it looks like the GS pay scale is in there

### 2014-2016 Data

Variable names are from this file (this is the file path after you unzip the entire dataset): `/opm-federal-employment-data/data/2014-09-to-2016-09/non-dod/documentation/Jeremy Singer-Vine Data Record Format.xls`. 

```{r}
dir2 = glue::glue("/Volumes/research_data/opm-federal-employment-data/data/", 
                  "2014-09-to-2016-09/non-dod/status/", "Non_DoD_201609.txt")


varnames = c("Family Name", "Given Name", "File Date", "Agency", "SubAgency", "State", "Age Range", "YSD (Year Since Degree) Range", "Education Level", "Pay Plan", "Grade", "LOS (Length of Service) Level", "Occupation", "Occupational Category (PATCO)", "Adjusted Basic Pay", "Supervisor", "TOA (Type of Appointment)", "Work Schedule", "NSFTP (Non-Seasonal Full-Time Permanent) Indicator")

df_pipe = read_delim(dir2, 
           col_names = varnames, col_types = cols(),
           delim = "|", na = c("", "NA", "*"), 
           n_max = 5000) 

df_pipe

```

